An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-09 paper.tex
Added participants section and table, closes #29.
- Added source to generate participants table.
- Added the generated table to the repo.
- Moved functions from py files into new utils.py.
- Added small text section in paper for participants info and embedded the
  table.

We collected over five and half hours of perturbed gait data from 11 subjects
sampled at 100 hz. The data has been organized and made available for other
research uses.

>>>>

We collected over five and half hours of perturbed gait data from 15 subjects
sampled at 100 hz. The data has been organized and made available for other
research uses.

\section*{Particpants}
%
Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
particpated in the study. The data has been anonymized with respect to the
participants' identities and an unique identification number was assigned to
each subject. A selection of the meta data collected for each subject is shown
in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns give the trial numbers associated with each nominal treadmill
    speed. Additional trials with subject 0 are trials with no subject, i.e.
    unloaded trials that can be used for force compensation purposes, and are
    not shown in the table. Generated by \verb|src/subject_table.py|.}
  \centering
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}
